Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
cut things we know will not appear

@@

@@

\break

\appendix

\section{Orphaned text}

In~our C++ work, the faults we encounter most frequently are
segmentation faults, 
memory errors caused by pointer arithmetic or uninitialized 
memory,
and heap exhaustion.
In~our Haskell work, the faults we encounter most frequently are
type errors and bounds-checking errors in array and vector accesses.
While we have found the bounds-checking errors difficult to debug,
they are less difficult than memory errors.

Implementing the equation in this form was not only intellectually
satisfying; it~also helped us find
bugs.
The most memorable bug was that in one of our base cases, 
we~mistakenly returned an empty path of states;
the correct result was a singleton path containing the initial state.
Very quickly after observing a missing state in the output, we were
able to find the faulty case in the code.

>>>>

\newif\iffinaldraft \finaldraftfalse % true if it's the final version

@@

\iffinaldraft

@@

\fi

%%%%    \break
%%%%    
%%%%    
%%%%    \appendix
%%%%    
%%%%    
%%%%    \section{Orphaned text}
%%%%    
%%%%    
%%%%    In~our C++ work, the faults we encounter most frequently are
%%%%    segmentation faults, 
%%%%    memory errors caused by pointer arithmetic or uninitialized 
%%%%    memory,
%%%%    and heap exhaustion.
%%%%    In~our Haskell work, the faults we encounter most frequently are
%%%%    type errors and bounds-checking errors in array and vector accesses.
%%%%    While we have found the bounds-checking errors difficult to debug,
%%%%    they are less difficult than memory errors.
%%%%    
%%%%    
%%%%    Implementing the equation in this form was not only intellectually
%%%%    satisfying; it~also helped us find
%%%%    bugs.
%%%%    The most memorable bug was that in one of our base cases, 
%%%%    we~mistakenly returned an empty path of states;
%%%%    the correct result was a singleton path containing the initial state.
%%%%    Very quickly after observing a missing state in the output, we were
%%%%    able to find the faulty case in the code.
%%%%    
%%%%    
%%%%
